Equalizer\\Programming and User Guide

### 2009-10-20 Developer/ProgrammingGuide/paper.tex
Update Programming Guide
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.0 for Equalizer 0.9+svn\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures \vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.7.0   & Sep 09, 2009 & Updates based on hardcopy print\\
    \hline
  \end{tabularx}}
\clearpage

@@

Equalizer provides a generic interface and implementation for the three
most common window systems through the OpenGL specific 
\textsf{eq::GLWindow} class: AGL, WGL and glX. The interfaces define the
minimal functionality needed to reuse other window system specific
classes, for example the AGL, WGL and glX event handlers. The separation 
of the OpenGL calls from the \textsf{OSWindow} permits to implement 
window systems which don't use any OpenGL context and therefore to use a 
different renderer. The implementation derived from these interfaces 
provides a sample implementation which honors all configurable window 
attributes.

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.1 for Equalizer 0.9+svn\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures \vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.7.0   & Sep 09, 2009 & Updates based on hardcopy print\\
    1.7.1   & Oct 20, 2009 & Updates for new eq::GLWindow\\
    \hline
  \end{tabularx}}
\clearpage

@@

Equalizer provides a generic interface and implementation for the three
most common window systems through the OpenGL specific 
\textsf{eq::GL\-Window} class: AGL, WGL and glX. The interfaces define the
minimal functionality needed to reuse other window system specific
classes, for example the AGL, WGL and glX event handlers. The separation 
of the OpenGL calls from the \textsf{OSWindow} permits to implement 
window systems which don't use any OpenGL context and therefore to use a 
different renderer. The implementation derived from these interfaces 
provides a sample implementation which honors all configurable window 
attributes.
